CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-28 codecheck-paper.tex
describe the "themes" of checks

The bulk of the certificates fall into three themes: (1) `classic'
papers from computational neuroscience (2) Covid modelling preprints
(3) AGILE.  We would like to briefly highlight three examples here.

@@

(DANIEL: say something about the Agile bundle, and the origins?)

>>>>

The bulk of the certificates fall into three themes: (1) `classic'
papers from computational neuroscience (2) Covid modelling preprints, and
(3) GIScience.  
The first theme was the initial set of papers used to explore the concept
of CODECHECK. The idea was to take very well known articles from a specific
domain, in this case the work area of co-author S.~Eglen, possibly as as a
conversation starter for potential collaborating journals.
The second theme is rather opportunistic. As the COVID-19 pandemic swept
over the whole Earth, we hoped to contribute to science's answer to the
unknown virus. The checks were solicited through community interaction.
The third theme represents co-author D.~N\"ust's work area.
Independent of CODECHECK, the \emph{Reproducible AGILE} Initiative \cite{reproducible_agile}
established a process for reproducing workflows at the AGILE conference
series. % TODO add reference to MUNIN talk
While using slightly different terms and infrastructue, e.g., `reproducibility
reports' are published on OSF, instead of certificates on Zenodo, the 
reproducibility reviews adhere to the codecheck principles.
Furthermore, two checks were completed as part of a peer review for a
GIScience journal.

Out of these areas, we would like to briefly highlight three examples here.

@@
